Positive Results in Registered Reports

### 2020-01-10 manuscript/manuscript.Rmd
1. added a robustness check to the quantitative analysis script, 2. reorganised the folder structure (in accordance with Psych-DS), 3. changed code in the manuscript Rmd and in the analysis scripts to accommodate the new folder structure, 4. added the preregistration document with comments indicating adherence/deviations, 5. added a file with the full list of Psych journals from the ESI database

```{r include = FALSE}
library("papaja")
library("bookdown")
library("rmarkdown")
library("knitr")
library("TOSTER")
library("purrr")
library("lattice")
library("ggplot2")
library("dplyr")
library("stringr")
library("reshape2")
```

@@

```{r include=FALSE}
source("interrater_agreement.R")
```

@@

### Hypothesis introductions
Selecting papers that use the phrase "test$^\ast$ the hypothes$^\ast$" might yield different results than alternative search phrases. 
Getting a better overview of "natural" descriptions of hypotheses would be useful for future investigations of the generalisability of Fanelli's [-@Fanelli2010] results and could inspire new research questions. 
We therefore extracted the phrase used to introduce the hypothesis from the coded hypothesis quotes for all RRs and tried to identify clusters of similar expressions which may be used to create alternative search phrases. 
If MS and AS had coded different hypothesis quotes for a paper, MS's coding was used, unless disagreement resolution of the "hypothesis support" variable lead to AS's coding overruling MS's.

@@

# Results
```{r include=FALSE}
source("quantitative_analyses.R")
```

@@

```{r include=FALSE}
source("hypothesis_introduction_analyses.R")
```
Finally, we analysed the language that was used to introduce or refer to hypotheses in RRs.
We were interested in whether the search phrase "test$^\ast$ the hypothes$^\ast$" used by Fanelli captured the way researchers write about hypothesis tests reasonably well. The answer is a resounding "no":
Searching the abstracts, titles, and keywords of the RR sample showed that only `r testthehypothes.RR`/`r n.RR` RRs would have been detected with this search phrase. 
To get an overview of analogous hypothesis-introduction phrases researchers used in RRs, we stripped the hypothesis quotes of RRs from all content-specific information and extracted "minimal" phrases that most distinctively indicated that a hypothesis was being described.
For example, from the hypothesis quote "(f)or Study 1, we predicted that participants reading about academic (vs. social) behaviors would show a better anagram performance" we extracted the hypothesis-introduction phrase "predicted that".

@@

```{r echo=FALSE, warning=FALSE, fig.width=6, fig.height=3, fig.cap="XXX ADD CAPTION"}
source("power_baserate_plot.R")
power.baserate.plot
```

>>>>

```{r include = FALSE}
library("papaja")
library("bookdown")
library("rmarkdown")
library("knitr")
library("TOSTER")
library("purrr")
library("lattice")
library("ggplot2")
library("dplyr")
library("stringr")
library("reshape2")
library("here")
```

@@

```{r include=FALSE}
source(here("analysis", "interrater_agreement.R"))
```

@@

### Hypothesis introductions
Selecting papers that use the phrase "test$^\ast$ the hypothes$^\ast$" might yield different results than alternative search phrases. 
Getting a better overview of "natural" descriptions of hypotheses would be useful for future investigations of the generalisability of Fanelli's [-@Fanelli2010] results and could inspire new research questions. 
We therefore extracted the phrase used to introduce the hypothesis from the coded hypothesis quotes for all RRs and tried to identify clusters of similar expressions which may be used to create alternative search phrases. .

@@

# Results
```{r include=FALSE}
source(here("analysis", "quantitative_analyses.R"))
```

@@

```{r include=FALSE}
source(here("analysis", "hypothesis_introduction_analyses.R"))
```
Finally, we analysed the language that was used to introduce or refer to hypotheses in RRs.
We were interested in whether the search phrase "test$^\ast$ the hypothes$^\ast$" used by Fanelli captured the way researchers write about hypothesis tests reasonably well. The answer is a resounding "no":
Searching the abstracts, titles, and keywords of the RR sample showed that only `r testthehypothes.RR`/`r n.RR` RRs would have been detected with this search phrase. 
To get an overview of analogous hypothesis-introduction phrases researchers used in RRs, we stripped the hypothesis quotes of RRs from all content-specific information and extracted "minimal" phrases that most distinctively indicated that a hypothesis was being described.
For example, from the hypothesis quote "(f)or Study 1, we predicted that participants reading about academic (vs. social) behaviors would show a better anagram performance" we extracted the hypothesis-introduction phrase "predicted that".

@@

```{r echo=FALSE, warning=FALSE, fig.width=6, fig.height=3, fig.cap="XXX ADD CAPTION"}
source(here("analysis", "power_baserate_plot.R"))
power.baserate.plot
```
